PyBOP: A Python package for battery model optimisation and parameterisation

### 2024-11-29 joss/paper.preprint.tex
Fix typos, update table format

\texttt{PyBOP} is a Python package designed to provide a user-friendly,
object-oriented interface for optimising battery models. \texttt{PyBOP}
leverages the open-source \texttt{PyBaMM} package
(\citeproc{ref-Sulzer:2021}{Sulzer et al., 2021}) to formulate and solve
of these battery models. \texttt{PyBOP} is intended to serve a broad
audience of students, engineers, and researchers in both academia and
the battery industry by enabling the use of predictive battery models
where previously this was not possible. \texttt{PyBOP} emphasises clear
and informative diagnostics and workflows for users of varying
expertise, by providing advanced optimisation and sampling algorithms.
These methods are provided through interfaces to \texttt{PINTS}
(\citeproc{ref-Clerx:2019}{Clerx et al., 2019}), \texttt{SciPy}
(\citeproc{ref-SciPy:2020}{Virtanen et al., 2020}), in addition to the
PyBOP's own algorithms such as Adaptive Moment Estimation with Weight
Decay (AdamW), Gradient descent, and Cuckoo search.

@@

\texttt{PyBOP} has a layered data structure designed to compute and
process the forward model predictions and to package the necessary
information for the optimisation and sampling algorithms. The forward
model is solved using the popular battery modelling package,
\texttt{PyBaMM}, with construction, parameterisation, and discretisation
managed by PyBOP's model interface to PyBaMM. This approach provides a
robust object construction process with a consistent interface between
the models and optimisers. The statistical methods and optimisation
algorithms are then constructed to interface cleanly with the forward
model predictions. Furthermore, identifiability metrics are provided
alongside the estimated parameters through Hessian approximation of the
cost functions in the frequentist workflows and posterior moments in the
Bayesian workflows.

@@

\texttt{PyBOP} formulates the inference process into four key classes,
namely the model, the problem, the cost, and the optimiser/sampler, as
shown in \autoref{fig:classes}. Each of these objects represents a base
class with child classes constructing specialised functionality for
inference or optimisation workflows. The model class constructs a
\texttt{PyBaMM} forward model for a given set of model equations
provided by \texttt{PyBaMM}, initial conditions, spatial discretisation,
and numerical solver. By composing \texttt{PyBaMM} directly into
\texttt{PyBOP}, specialised models can be constructed alongside the
standard models, which can be modified, and optimally constructed for
the inference tasks. One such example is spatial rediscretisation, which
is performed when geometric parameters are optimised. In this situation,
\texttt{PyBOP} minimally rediscretises the \texttt{PyBaMM} model while
maintaining the problem, cost, and optimiser objects, providing improved
performance benefits to users. Alongside construction of the forward
model, \texttt{PyBOP}`s model class provides methods for obtaining
sensitivities from the prediction, enabling gradient-based optimisation
algorithms. This prediction, along with it's corresponding
sensitivities, is provided to the problem class for processing and
exception control. A standardised data structure is then provided to the
cost classes, providing a distance, design, or likelihood-based metric
for optimisation. For deterministic optimisation, the optimisers
minimise the corresponding cost function or the negative log-likelihood
if a likelihood class is provided. Bayesian inference is provided by
Monte Carlo sampling classes, which accept the LogPosterior class and
sample from it using Pints' based Monte Carlo algorithms at the time of
submission. In the typical workflow, the classes in
\autoref{fig:classes} are constructed in sequence.

In addition to the core architecture, \texttt{PyBOP} provides several
specialised inference and optimisation processes. One such instance is
numerical electrochemical impedance spectroscopy predictions by
discretising the forward model into sparse mass matrix form with
accompanying auto-differentiated Jacobian. These objects are then
translated into the frequency domain with a linear solution used to
compute the battery model impedance. In this situation, the forward
models are constructed within the spatial rediscretisation workflow,
allowing for geometric parameter inference from EIS forward model
predictions. Furthermore, \texttt{PyBOP} builds on the JAX
(\citeproc{ref-jax:2018}{Bradbury et al., 2018}) numerical solvers
provided by \texttt{PyBaMM} by providing JAX-based cost functions for
automatic forward model differentiation with respect to the parameters.
This functionality provides a performance improvement alongside an
interface to JAX-based inference packages, such as Numpyro
(\citeproc{ref-numpyro:2019}{Phan et al., 2019}), BlackJAX
(\citeproc{ref-blackjax:2024}{Cabezas et al., 2024}), and Optax
(\citeproc{ref-optax:2020}{DeepMind et al., 2020}).

@@

The currently implemented subclasses for the model, problem, and cost
classes are listed in \autoref{tab:subclasses}. The cost functions are
grouped by problem type, while the model and optimiser classes can be
selected in combination with any problem-cost pair.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4458}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2048}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3494}}@{}}
\caption{List of available model, problem and cost (or likelihood)
classes. \label{tab:subclasses}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Battery Models
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Problem Types
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cost / Likelihood Functions
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Battery Models
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Problem Types
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cost / Likelihood Functions
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Single particle model (SPM) & Fitting problem & Sum squared error \\
SPM with electrolyte (SPMe) & & Root mean squared error \\
Doyle-Fuller-Newman (DFN) & & Minkowski \\
Many particle model (MPM) & & Sum of power \\
Multi-species multi-reaction (MSMR) & & Gaussian log likelihood \\
Weppner Huggins & & Maximum a posteriori \\
Equivalent circuit model (ECM) & Observer & Unscented Kalman filter \\
& Design problem & Gravimetric energy density \\
& & Volumetric energy density \\
\end{longtable}

Similarly, the current algorithms available for optimisation tasks are
presented in \autoref{tab:optimisers}. From now on, the point-based
parameterisation and design optimisation tasks will simply be referred
to as optimisation tasks. This simplification can be justified by
examining \autoref{eqn:parameterisation} and \autoref{eqn:design} and
confirming that deterministic parameterisation can be viewed as an
optimisation task to minimise a distance-based cost function.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4062}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2604}}@{}}
\caption{The currently supported optimisation algorithms classified by
candidate solution type, including gradient information. (*) Scipy
minimize has gradient and non-gradient methods.
\label{tab:optimisers}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
(Meta)heuristic
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
(Meta)heuristic
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Weight decayed adaptive moment estimation (AdamW) & Covariance matrix
adaptation (CMA-ES) & Particle swarm (PSO) \\
Improved resilient backpropagation (iRProp-) & Exponential natural
(xNES) & Nelder-Mead \\
Gradient descent & Separable natural (sNES) & Cuckoo search \\
SciPy minimize (*) & SciPy differential evolution & \\
& & \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1810}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2155}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1379}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2069}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2586}}@{}}
\caption{Sampling methods supported by PyBOP, classified according to
the proposed method. \label{tab:samplers}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Adaptive
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Slicing
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Adaptive
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Slicing
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Monomial Gamma & Delayed Rejection Adaptive & Rank Shrinking &
Differential Evolution & Metropolis Random Walk \\
No-U-Turn & Haario Bardenet & Doubling & & Emcee Hammer \\
Hamiltonian & Haario & Stepout & & Metropolis Adjusted Langevin \\
Relativistic & Rao Blackwell & & & \\
\end{longtable}

@@

This parameterisation task can also be approached from a Bayesian
perspective, which we will present below using PyBOP's sampler methods.
The optimisation equation presented in equation
\autoref{eqn:parameterisation} does not represent the Bayesian parameter
identification task, and as such we introduce the Bayes theorem as,

@@

where, \(P(\theta|D)\) is the posterior and represents the probability
density function of the parameter. \(P(D|\theta)\) is the likelihood
function and assesses the parameter values alongside a noise model.
\(P(\theta)\) encapsulates the prior knowledge about the parameters, and
finally \(P(D)\) is the model evidence and acts as a normalising
constant so that the final posterior is a correctly scaled density
function. Our goal in parameter inference is to identify the parameter
values with the highest probability, which can be represented as a
point-based metric or as the posterior distribution, which provides
additional information about the uncertainty of the identified
parameters. Monte Carlo sampling methods are available to obtain this
posterior distribution. These methods sample from the posterior using a
variety of methods, including gradient-based methods such as No-U-Turn
(\citeproc{ref-NUTS:2011}{Hoffman \& Gelman, 2011}) and Hamiltonian
(\citeproc{ref-Hamiltonian:2011}{Brooks et al., 2011}), as well as
heuristic methods such as Differential Evolution
(\citeproc{ref-DiffEvolution:2006}{Braak, 2006}), and finally
conventional methods based on random sampling with rejection criteria
(\citeproc{ref-metropolis:1953}{Metropolis et al., 1953}). PyBOP offers
a sampling class that provides an interface to these samplers, which are
supported by the Probabilistic Inference of Noise Time-Series (PINTS)
package. \autoref{fig:posteriors} below shows the sampled posterior for
the synthetic workflow described above, using an adaptive
covariance-based sampler, Haario Bardenet
(\citeproc{ref-Haario:2001}{Haario et al., 2001}).

>>>>

\texttt{PyBOP} is a Python package designed to provide a user-friendly,
object-oriented interface for optimising battery models. \texttt{PyBOP}
leverages the open-source \texttt{PyBaMM} package
(\citeproc{ref-Sulzer:2021}{Sulzer et al., 2021}) to formulate and solve
of these battery models. \texttt{PyBOP} is intended to serve a broad
audience of students, engineers, and researchers in both academia and
the battery industry by enabling the use of predictive battery models
where previously this was not possible. \texttt{PyBOP} emphasises clear
and informative diagnostics and workflows for users of varying
expertise, by providing advanced optimisation and sampling algorithms.
These methods are provided through interfaces to \texttt{PINTS}
(\citeproc{ref-Clerx:2019}{Clerx et al., 2019}), \texttt{SciPy}
(\citeproc{ref-SciPy:2020}{Virtanen et al., 2020}), in addition to the
\texttt{PyBOP}'s own algorithms such as Adaptive Moment Estimation with
Weight Decay (AdamW), Gradient descent, and Cuckoo search.

@@

\texttt{PyBOP} has a layered data structure designed to compute and
process the forward model predictions and to package the necessary
information for the optimisation and sampling algorithms. The forward
model is solved using the popular battery modelling package,
\texttt{PyBaMM}, with construction, parameterisation, and discretisation
managed by \texttt{PyBOP}'s model interface to \texttt{PyBaMM}. This
approach provides a robust object construction process with a consistent
interface between the models and optimisers. The statistical methods and
optimisation algorithms are then constructed to interface cleanly with
the forward model predictions. Furthermore, identifiability metrics are
provided alongside the estimated parameters through Hessian
approximation of the cost functions in the frequentist workflows and
posterior moments in the Bayesian workflows.

@@

\texttt{PyBOP} formulates the inference process into four key classes,
namely the model, the problem, the cost, and the optimiser/sampler, as
shown in \autoref{fig:classes}. Each of these objects represents a base
class with child classes constructing specialised functionality for
inference or optimisation workflows. The model class constructs a
\texttt{PyBaMM} forward model for a given set of model equations
provided by \texttt{PyBaMM}, initial conditions, spatial discretisation,
and numerical solver. By composing \texttt{PyBaMM} directly into
\texttt{PyBOP}, specialised models can be constructed alongside the
standard models, which can be modified, and optimally constructed for
the inference tasks. One such example is spatial rediscretisation, which
is performed when geometric parameters are optimised. In this situation,
\texttt{PyBOP} minimally rediscretises the \texttt{PyBaMM} model while
maintaining the problem, cost, and optimiser objects, providing improved
performance benefits to users. Alongside construction of the forward
model, \texttt{PyBOP}'s model class provides methods for obtaining
sensitivities from the prediction, enabling gradient-based optimisation
algorithms. This prediction, along with it's corresponding
sensitivities, is provided to the problem class for processing and
exception control. A standardised data structure is then provided to the
cost classes, providing a distance, design, or likelihood-based metric
for optimisation. For deterministic optimisation, the optimisers
minimise the corresponding cost function or the negative log-likelihood
if a likelihood class is provided. Bayesian inference is provided by
Monte Carlo sampling classes, which accept the LogPosterior class and
sample from it using \texttt{PINTS} based Monte Carlo algorithms at the
time of submission. In the typical workflow, the classes in
\autoref{fig:classes} are constructed in sequence.

In addition to the core architecture, \texttt{PyBOP} provides several
specialised inference and optimisation processes. One such instance is
numerical electrochemical impedance spectroscopy predictions by
discretising the forward model into sparse mass matrix form with
accompanying auto-differentiated Jacobian. These objects are then
translated into the frequency domain with a linear solution used to
compute the battery model impedance. In this situation, the forward
models are constructed within the spatial rediscretisation workflow,
allowing for geometric parameter inference from EIS forward model
predictions. Furthermore, \texttt{PyBOP} builds on the \texttt{JAX}
(\citeproc{ref-jax:2018}{Bradbury et al., 2018}) numerical solvers
provided by \texttt{PyBaMM} by providing \texttt{JAX}-based cost
functions for automatic forward model differentiation with respect to
the parameters. This functionality provides a performance improvement
alongside an interface to JAX-based inference packages, such as
\texttt{Numpyro} (\citeproc{ref-numpyro:2019}{Phan et al., 2019}),
\texttt{BlackJAX} (\citeproc{ref-blackjax:2024}{Cabezas et al., 2024}),
and \texttt{Optax} (\citeproc{ref-optax:2020}{DeepMind et al., 2020}).

@@

The currently implemented subclasses for the model, problem, and cost
classes are listed in \autoref{tab:subclasses}. The model and optimiser
classes can be selected in combination with any problem-cost pair.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4458}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2048}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3494}}@{}}
\caption{List of available model, problem and cost (or likelihood)
classes. \label{tab:subclasses}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Battery Models
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Problem Types
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cost / Likelihood Functions
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Battery Models
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Problem Types
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cost / Likelihood Functions
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Single particle model (SPM) & Fitting problem & Sum squared error \\
SPM with electrolyte (SPMe) & Design problem & Root mean squared
error \\
Doyle-Fuller-Newman (DFN) & Observer & Minkowski \\
Many particle model (MPM) & & Sum of power \\
Multi-species multi-reaction (MSMR) & & Gaussian log likelihood \\
Weppner Huggins & & Maximum a posteriori \\
Equivalent circuit model (ECM) & & Volumetric energy density \\
& & Gravimetric energy density \\
& & Unscented Kalman filter \\
\end{longtable}

Similarly, the current algorithms available for optimisation tasks are
presented in \autoref{tab:optimisers}. It should be noted that
\texttt{SciPy} minimize has gradient and non-gradient methods. From now
on, the point-based parameterisation and design optimisation tasks will
simply be referred to as optimisation tasks. This simplification can be
justified by examining \autoref{eqn:parameterisation} and
\autoref{eqn:design} and confirming that deterministic parameterisation
can be viewed as an optimisation task to minimise a distance-based cost
function.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4722}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2963}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2315}}@{}}
\caption{The currently supported optimisation algorithms classified by
candidate solution type, including gradient information.
\label{tab:optimisers}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
(Meta)heuristic
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
(Meta)heuristic
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Weight decayed adaptive moment estimation (AdamW) & Covariance matrix
adaptation (CMA-ES) & Particle swarm (PSO) \\
Improved resilient backpropagation (iRProp-) & Exponential natural
(xNES) & Nelder-Mead \\
Gradient descent & Separable natural (sNES) & Cuckoo search \\
SciPy minimize & SciPy differential evolution & \\
& & \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1810}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2155}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1379}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2069}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2586}}@{}}
\caption{Sampling methods supported by \texttt{PyBOP}, classified
according to the proposed method. \label{tab:samplers}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Adaptive
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Slicing
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gradient-based
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Adaptive
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Slicing
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Evolutionary
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Monomial Gamma & Delayed Rejection Adaptive & Rank---Shrinking &
Differential Evolution & Metropolis Random Walk \\
No-U-Turn & Haario Bardenet & Doubling & & Emcee Hammer \\
Hamiltonian & Haario & Stepout & & Metropolis Adjusted Langevin \\
Relativistic & Rao Blackwell & & & \\
\end{longtable}

@@

This parameterisation task can also be approached from a Bayesian
perspective, which we will present below using \texttt{PyBOP}'s sampler
methods. The optimisation equation presented in equation
\autoref{eqn:parameterisation} does not represent the Bayesian parameter
identification task, and as such we introduce the Bayes theorem as,

@@

where, \(P(\theta|D)\) is the posterior and represents the probability
density function of the parameter. \(P(D|\theta)\) is the likelihood
function and assesses the parameter values alongside a noise model.
\(P(\theta)\) encapsulates the prior knowledge about the parameters, and
finally \(P(D)\) is the model evidence and acts as a normalising
constant so that the final posterior is a correctly scaled density
function. Our goal in parameter inference is to identify the parameter
values with the highest probability, which can be represented as a
point-based metric or as the posterior distribution, which provides
additional information about the uncertainty of the identified
parameters. Monte Carlo sampling methods are available to obtain this
posterior distribution. These methods sample from the posterior using a
variety of methods, including gradient-based methods such as No-U-Turn
(\citeproc{ref-NUTS:2011}{Hoffman \& Gelman, 2011}) and Hamiltonian
(\citeproc{ref-Hamiltonian:2011}{Brooks et al., 2011}), as well as
heuristic methods such as Differential Evolution
(\citeproc{ref-DiffEvolution:2006}{Braak, 2006}), and finally
conventional methods based on random sampling with rejection criteria
(\citeproc{ref-metropolis:1953}{Metropolis et al., 1953}).
\texttt{PyBOP} offers a sampling class that provides an interface to
these samplers, which are supported by the Probabilistic Inference of
Noise Time-Series (\texttt{PINTS}) package. \autoref{fig:posteriors}
below shows the sampled posterior for the synthetic workflow described
above, using an adaptive covariance-based sampler, Haario Bardenet
(\citeproc{ref-Haario:2001}{Haario et al., 2001}).
